Bayesim: a tool for fast device characterization with Bayesian inference

### 2018-06-29 paper/Manuscript.tex
add doc

%File Generated with PyPaper
\documentclass[aps,prl,reprint,amsmath,amssymb,superscriptaddress,notitlepage,groupedaddress]{revtex4-1}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{stackengine}
\usepackage[section]{placeins}
\usepackage[dvipsnames*,svgnames]{xcolor}
\usepackage{verbatim}
\usepackage[position=bottom,caption=false,captionskip=3pt,font=normalsize,subrefformat=simple,labelformat=simple]{subfig}
\renewcommand{\thesubfigure}{(\alph{subfigure})}
\usepackage{listings}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{chngcntr}
\usepackage{bm}
\usepackage{url}
\def\UrlBreaks{\do\/\do-}
\newcommand {\framedgraphic}[2] {\begin{frame}{#1}\begin{center}\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{#2}\end{center}\end{frame}}\usepackage[breaklinks]{hyperref}
\usepackage{breakurl}
\usepackage{tabularx}
\usepackage{soul}
\hypersetup{
colorlinks,
linkcolor={blue!100!black},
citecolor={blue},
urlcolor={blue!80!black}}
\lstset{basicstyle=\small\ttfamily,columns=flexible,breaklines=true}\newcommand{\fakesection}[1]{\par\refstepcounter{section}\sectionmark{#1}\addcontentsline{toc}{section}{\protect\numberline{\thesection}#1}}\def\equationautorefname~#1\null{#1\null}
\raggedbottom\usepackage[bottom]{footmisc} \makeatletter \def\p@section{} \def\p@subsubsection{} \makeatother\begin{document}
\title{Bayesim: a tool for fast device characterization with Bayesian inference}
\author{Rachel Kurchin}
\affiliation{Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
\author{Giuseppe Romano}
\affiliation{Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
\author{Tonio Buonassisi}
\email{buonassi@mit.edu}
\affiliation{Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
\begin{abstract}
Target journal: Computer Physics Communications\end{abstract}
\maketitle

@@

\section*{Software Architecture and Interface}
 \begin{itemize}\item description of structure of new code and workflow for using it (both Python scripting and command-line) \item figure 2 \end{itemize}  \begin{figure}
{\includegraphics[width=0.7\columnwidth]{././figure_2.png}}
\caption{Bayesian workflow}
\end{figure}
\section*{Application Examples}
 \subsection{Ideal Diode Model}
  \begin{itemize}\item validation example - ``observed'' data is just generated using the model and we show we can recover the correct input parameters \item figure 3 showing PMF (animation in ESI) \end{itemize}  \begin{figure}
{\includegraphics[width=0.7\columnwidth]{././figure_3.png}}
\caption{Ideal diode}
\end{figure}\subsection{Example with Real Data}
  \begin{itemize}\item more practical example - probably fitting resistive diode to the same SnS data we used in the Joule paper \item figure 4 showing PMF (animation in ESI) and comparison of JV curves \end{itemize}  
\begin{figure}[!ht]

>>>>

%File Generated with PyPaper
\documentclass[aps,prl,reprint,amsmath,amssymb,superscriptaddress,notitlepage,groupedaddress]{revtex4-1}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{stackengine}
\usepackage[section]{placeins}
\usepackage[dvipsnames*,svgnames]{xcolor}
\usepackage{verbatim}
\usepackage[position=bottom,caption=false,captionskip=3pt,font=normalsize,subrefformat=simple,labelformat=simple]{subfig}
\renewcommand{\thesubfigure}{(\alph{subfigure})}
\usepackage{listings}
\usepackage{mathtools}
\usepackage{todonotes}
\usepackage{amsmath}
\usepackage{chngcntr}
\usepackage{bm}
\usepackage{url}
\def\UrlBreaks{\do\/\do-}
\newcommand {\framedgraphic}[2] {\begin{frame}{#1}\begin{center}\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{#2}\end{center}\end{frame}}\usepackage[breaklinks]{hyperref}
\usepackage{breakurl}
\usepackage{tabularx}
\usepackage{soul}
\hypersetup{
colorlinks,
linkcolor={blue!100!black},
citecolor={blue},
urlcolor={blue!80!black}}
\lstset{basicstyle=\small\ttfamily,columns=flexible,breaklines=true}\newcommand{\fakesection}[1]{\par\refstepcounter{section}\sectionmark{#1}\addcontentsline{toc}{section}{\protect\numberline{\thesection}#1}}\def\equationautorefname~#1\null{#1\null}
\raggedbottom\usepackage[bottom]{footmisc} \makeatletter \def\p@section{} \def\p@subsubsection{} \makeatother\begin{document}
\title{Bayesim: a tool for fast device characterization with Bayesian inference}
\author{Rachel Kurchin}
\affiliation{Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
\author{Giuseppe Romano}
\affiliation{Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
\author{Tonio Buonassisi}
\email{buonassi@mit.edu}
\affiliation{Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
\begin{abstract}
Target journal: Computer Physics Communications\end{abstract}
\maketitle

@@

\section*{Software Architecture and Interface}
 \begin{itemize}\item description of structure of new code and workflow for using it (both Python scripting and command-line) \item figure 2 \end{itemize}  \begin{figure}
{\includegraphics[width=0.7\columnwidth]{././figure_2.png}}
\caption{Bayesian workflow}
\end{figure}
\section*{Application Examples}
 \subsection{Ideal Diode Model}
  \begin{itemize}\item validation example - ``observed'' data is just generated using the model and we show we can recover the correct input parameters \item figure 3 showing PMF (animation in ESI) \end{itemize}  \begin{figure}
{\includegraphics[width=0.7\columnwidth]{././figure_3.png}}
\caption{Ideal diode}
\end{figure}\subsection{Example with Real Data}
  \begin{itemize}\item more practical example - probably fitting resistive diode to the same SnS data we used in the Joule paper \item figure 4 showing PMF (animation in ESI) and comparison of JV curves \end{itemize} \todo[inline]{example fgryer2qt rt r}  
\begin{figure}[!ht]
